### 2016-04-07 ch02-qlogms/excitation-design.tex
Plots with grid summaries

  \begin{figure}[ht]
    \centering
      \remakeNextFigure
      \setlength\figurewidth{0.8\columnwidth}
      \setlength\figureheight{0.5\figurewidth}
    \input{\thisDir/figs/freqGrid.tikz}
    \caption[Amplitude spectrum for linear, logarithmic, quasi-logarithmic grids.]{Comparison of the amplitude spectrum of a linear grid multisine, a logarithmic grid multisine, the compensated quasi-logarithmic multisine and the `pink' quasi-log multisine.
    $\omegaLinLog$ indicates the cross-over between the linear and logarithmic regions. }%
    \label{fig:excitation:freqGrids}
  \end{figure}

  \begin{table}
  \centering
   \caption{Summary of  properties of the different frequency grids.}
    \begin{tabular}{rccc} 
    \toprule
     & \textsc{Linear} & \textsc{Logarithmic} & \textsc{Quasi-logarithmic} \\
    \midrule
    % Limits & \multicolumn{3}{c}{$\ClosedInterval{\fMin, \fMax}$}\\
    Properties 
       & $f_0, \Delta f$ 
       & $f_0, \alpha$ 
       & $f_0, \Delta f, \alpha$\\
    \midrule
    $f_{k+1} \isdef$ 
       & $f_{k} + \Delta f$ 
       & $\alpha f_{k}$
       & $\round{\frac{\alpha^{N_k} f_k}{\Delta f}} \Delta f$,   $N_k \in \NaturalNumbersWithoutZero$
       \\[5pt]
    $\Delta f_k \isdef f_{k+1} - f_k$ 
       & $\Delta f$
       & $(\alpha - 1) f_k$
       & $ \in \NaturalNumbersWithoutZero \Delta f$ \\[5pt]
    $\alpha_k \isdef \frac{f_{k+1}}{f_k}$ 
       & $1 + \frac{\Delta f}{f_k}$ 
       & $\alpha$ 
       & $\approx \alpha $ \\[5pt]
    $F_{\ClosedInterval{a,b}}$
       & $\floor{\frac{b - a}{\Delta f}}$
       & $\floor{\log_{\alpha} \frac{b}{a}}$
       & $\approx \floor{\log_{\alpha} \frac{b}{a}}$\\[5pt]
    $F_{\ClosedInterval{f, \kappa f}}$
      & $\floor{\frac{(\kappa - 1)f}{\Delta f}}$
      & $\floor{\log_{\alpha} \kappa}$
      & $\approx \floor{\log_{\alpha} \kappa}$\\[5pt]
    \bottomrule
    \end{tabular}
  \end{table}

  \TODO{plot: $\alpha $ (evt. $\cdot A_k^2$) i.f.v. $\omega$ voor verschillende signalen.}
  \TODO{plot: $\Delta f $ i.f.v. $\omega$ voor verschillende signalen} 
  \TODO{plot: $\# \omega / \mathrm{decade}$ i.f.v. $\omega$ voor verschillende signalen}

  At the lowest frequencies the quasi-log grid and the linear grid frequencies do coincide and each line in the quasi-log grid is surrounded by many lines of the log grid.
  The amplitudes of the compensated and pink quasi-log lines show that the compensation only has effect at the lower frequencies since the uncompensated counterpart has an amplitude spectrum close to $1$.
  We can expect a very similar behavior from properly designed compensated quasi-log multisines and from the `pink' quasi-log multisine, since their amplitude spectra are almost identical.
  As such, it is advised to use `pink' quasi-log multisines as those can be constructed using more straightforward code (equation \eqref{eq:excitation:pink}) than the compensated quasi-log multisines (equations \eqref{eq:excitation:nfk}, \eqref{eq:excitation:nearestLines} , and \eqref{eq:excitation:compensationAk}).
  %TODO: mention crest factor? (here compensation/pink hurts)

>>>>

  \begin{figure}[ht]
    \centering
      \setlength\figurewidth{0.8\columnwidth}
      \setlength\figureheight{0.5\figurewidth}
    \input{\thisDir/figs/freqGrid.tikz}
    \caption[Amplitude spectrum for linear, logarithmic, quasi-logarithmic grids.]{Comparison of the amplitude spectrum of a linear grid multisine, a logarithmic grid multisine, the compensated quasi-logarithmic multisine and the `pink' quasi-log multisine.
    $\omegaLinLog$ indicates the cross-over between the linear and logarithmic regions. }%
    \label{fig:excitation:freqGrids}
  \end{figure}

  \begin{table}
  \centering
  \label{tbl:excitation:gridProperties}
   \caption{Summary of  properties of the different frequency grids.}
    \begin{tabular}{rccc} 
    \toprule
     & \textsc{Linear} & \textsc{Logarithmic} & \textsc{Quasi-logarithmic} \\
    \midrule
    % Limits & \multicolumn{3}{c}{$\ClosedInterval{\fMin, \fMax}$}\\
    Properties 
       & $f_0, \Delta f$ 
       & $f_0, \alpha$ 
       & $f_0, \Delta f, \alpha$\\
    \midrule
    $f_{k+1} \isdef$ 
       & $f_{k} + \Delta f$ 
       & $\alpha f_{k}$
       & $\round{\frac{\alpha^{N_k} f_k}{\Delta f}} \Delta f$,   $N_k \in \NaturalNumbersWithoutZero$
       \\[5pt]
    $\Delta f_k \isdef f_{k+1} - f_k$ 
       & $\Delta f$
       & $(\alpha - 1) f_k$
       & $ \in \NaturalNumbersWithoutZero \Delta f$ \\[5pt]
    $\alpha_k \isdef \frac{f_{k+1}}{f_k}$ 
       & $1 + \frac{\Delta f}{f_k}$ 
       & $\alpha$ 
       & $\approx \alpha $ \\[5pt]
    $F_{\ClosedInterval{a,b}}$
       & $\floor{\frac{b - a}{\Delta f}}$
       & $\floor{\log_{\alpha} \frac{b}{a}}$
       & $\approx \floor{\log_{\alpha} \frac{b}{a}}$\\[5pt]
    $F_{\ClosedInterval{f, \kappa f}}$
      & $\floor{\frac{(\kappa - 1)f}{\Delta f}}$
      & $\floor{\log_{\alpha} \kappa}$
      & $\approx \floor{\log_{\alpha} \kappa}$\\[5pt]
    \bottomrule
    \end{tabular}
  \end{table}

  \begin{figure}
    \centering
    \setlength\figurewidth{0.85\columnwidth}
    \setlength\figureheight{0.68\figurewidth}
    \input{\thisDir/figs/gridProps.tikz}
    \caption[Actual frequency grid spacing and ratio for different grids]{Actual frequency grid spacing $\Delta f_k$ and ratio $\alpha_k$ as a function of the frequency, for the different grid types with $f_0 =1\unit{Hz}$, $\Delta f = 1\unit{Hz}$ and $\alpha =1.05$ as in \figref{fig:excitation:freqGrids}. $\omegaLinLog$ marks the transition between linear and logarithmic regime in the quasi-logarithmic grid.}
    \label{fig:excitation:gridPropertyPlots}
  \end{figure}

  At the lowest frequencies the quasi-log grid and the linear grid frequencies do coincide and each line in the quasi-log grid is surrounded by many lines of the log grid.
  The amplitudes of the compensated and pink quasi-log lines show that the compensation only has effect at the lower frequencies since the uncompensated counterpart has an amplitude spectrum close to $1$.
  The properties of these frequency grids are summarized in \tabref{tbl:excitation:gridProperties} and \figref{fig:excitation:gridPropertyPlots}.

  We can expect a very similar behavior from properly designed compensated quasi-log multisines and from the `pink' quasi-log multisine, since their amplitude spectra are almost identical.
  As such, it is advised to use `pink' quasi-log multisines as those can be constructed using more straightforward code (equation \eqref{eq:excitation:pink}) than the compensated quasi-log multisines (equations \eqref{eq:excitation:nfk}, \eqref{eq:excitation:nearestLines} , and \eqref{eq:excitation:compensationAk}).
  %TODO: mention crest factor? (here compensation/pink hurts)
